# my little reminder...
***
# ...how to import text files into R
***

### (this bare bone example is dealing with *.csv but almost the same apply for other text file types)

## setwd and define the vector of filenames
```{r}
#setwd("/some_dir/import_files")

filenames <- list.files(pattern=".csv")
```
****
## case 1 - assign each file to a separate data frame...

### ...and name each data frame as the file name
```{r}
for(i in filenames) {
  assign(i, read.csv(i, header=TRUE, sep="\t"))  
}
```

### ...and name each data frame by prepending "df_" to the file name
```{r}
for(i in filenames) {
  assign(paste0("df_",i), read.csv(i, header=TRUE, sep="\t"))  
}
```

### ...and name each data frame by prepending "df_" and removing the file extension
```{r}
for(i in filenames) {
  assign(paste0("df_", gsub(".csv","", i)), read.csv(i, header=TRUE, sep="\t"))  
}
```
****
## case 2 - merge all files into a single data frame...

### ...with the use of a for loop

```{r}
df<-NULL #df<-c() #alternative
for(i in filenames) {
   df<-rbind(df,read.csv(i, header=TRUE, sep="\t"))  
}
```

### ...with the use of functions lapply and do.call
```{r}
df<-do.call("rbind", lapply(filenames, read.csv, header = TRUE, sep="\t")) 
```

